%\vspace*{\fill}
\chapter*{Abstract}
Causal questions seek to determine whether there exists a causal relationship 
between different events or phenomena. 
Specifically, they often aim to understand the underlying causes of an effect or what kind of effects a particular cause might have in the future.
Causal questions are important for various use cases, for example, in virtual assistants or search engines.
However, many current approaches to causal question answering cannot provide explanations or verifications for their answers. 
Additionally, the approaches were often missing 
large-scale datasets of causal relations.
In this thesis, we explore the application of reinforcement learning on CauseNet, a large-scale causal knowledge graph, to answer binary causal questions inspired by the successful application of reinforcement learning in knowledge graph tasks, such as link prediction and fact-checking.
We introduce an Actor-Critic based agent which learns to search through the graph to answer binary causal questions.
Additionally, we bootstrap the agent with a supervised learning procedure and adapt an existing reward shaping strategy to deal 
with large action spaces and sparse rewards.
Our evaluation shows that our agent successfully prunes the search to answer binary causal questions efficiently.
Moreover, our ablation study indicates that the supervised learning strategy provides a strong foundation upon which the agent can improve.
Finally, we demonstrate how the paths learned by the agent can be used to explain causal relations, to indicate the specific mechanisms by which a cause produces an effect.
%\vspace*{\fill}